Formalizing Stack Safety as a Security Property

### 2023-01-23 submission5/core.tex
Reorg and closer edits

We propose a novel characterization of stack safety using the formal tools of language-based
security~\cite{sabelfeld2003language}, decomposing stack safety into
the {\em integrity} and {\em confidentiality} of the caller’s local state
during the callee's execution, the confidentiality of the callee's local state
afterward, and the control flow protection of {\em well-bracketed control
  flow (WBCF)}~\cite{SkorstengaardSTKJFP}. We also extend WBCF to a setting with exceptions,
in which there may be multiple points at which a callee can ``return.''

@@

We treat stack safety as multiple properties, rather than one multi-faceted property, because
not all enforcement mechanisms attempt to implement all aspects of stack safety. Some focus
exclusively on control flow, others protect the confidentiality of the caller but not the
callee, etc.

@@

Roessler and DeHon find that the intuitive way to enforce stack safety in this setting
is inefficient when allocating and clearing stack frames, because each word must be initialized
with a tag corresponding to the (depth of the) current function activation. They propose
{\em Lazy Tagging and Clearing}, in which tags are not initialized at allocation, but only
when a function writes to memory. This means that such writes cannot be protected. Instead
the micro-policy enforces that memory be read by the same fuction that wrote it. This
lazy enforcement is incompatible with existing models of stack safety,
because an attacker can modify another function's data. But the owner of
the data will never see the changes, so it is secure in the sense that the attacker is
unsuccessful at changing program behavior (except, perhaps, by causing a fault.) We aim to elaborate
that sense, and to test whether the micro-policy fulfills it.

This key motivation leads us to present integrity and confidentiality as predicates on (pairs of)
machine states that make claims about the future observable behavior of execution from those states.
That is not to say that our properties are specialized for lazy micro-policies. It also supports
normal ``eager'' micro-policies, and should support other enforcement mechanisms. In fact, our
observational properties are even weaker than necessary to support Roessler and Dehon's micro-policy.

@@

\begin{itemize}
\item We formalize permissive stack confidentiality and integrity properties.
  Both are parameterized over a notion of external
  observation, and are violated only if accessing secrets or overwriting
  data causes a visible change in system behavior.
\item We instantiate these definitions with a realistic
  system with features such as argument passing
  on the stack, callee-saves registers, and tail-call elimination.
  Our model is modular enough that adding these features is straightforward.
\item Our formalization of well-bracketed control flow in the presence of tail-call
  elimination is a slight novelty over existing models.
\item We use property-based random testing to validate the relationship between
  our properties and micro-policies.
\end{itemize}

@@

The set of security-relevant operations (\(\Psi\)) covered in this paper is given in
\cref{tab:psi}. Those that we explore in detail in \cref{sec:example}
are shown in white: calls, returns, and the allocation and deallocation of local memory.
In \cref{sec:machine}), we cover additional operations add parameters to the examples', to support
various forms of memory sharing and tail-call elimination. These are shown in light gray.
We give a proof-of-concept formalization of a more sophisticated, heap-like sharing model
based on pointer provenance in \cref{app:ptr}, represented by the dark grey
operations, but we do not test this.

@@

@@

We have five different properties to introduce:

\begin{itemize}
\item Well=bracketed Control Flow (\(WBCF\))
\item Caller Integrity (\(CLRI\))
\item Caller Confidentiality (\(CLRC\))
\item Callee Confidentiality (\(CLEC\))
\item Callee Integrity (\(CLEI\))
\end{itemize}

The properties form a rough hierarchy; although they are technically separate and need
not coexist in any particular combination, some are likely to take priority in terms of their
importance to security. Almost all stack-safety enforcement mechanisms will try to enforce \(WBCF\),
as control-flow attacks such as ROP are a major vulnerability that can be targeted via the stack.
Many also cover some degree of (caller) integrity. [TODO: more hierarchy].

@@

Otherwise, we do not assume that the code adheres to any particular
calling convention or implements a source language construct.
In particular, while we are agnostic as to the source
language, we certainly aim to support C, and so any source function might contain undefined
behavior resulting in its compilation to arbitrary machine code. A given enforcement
mechanism may place additional constraints, particularly on the behavior of
call and return sequences.

@@

The security semantics for this program is based
on the security-relevant events noted in the right columns of Figures~\ref{fig:main}
and~\ref{fig:f}, namely execution of instructions that allocate or deallocate space,
make a call, or make a return.
Figure \ref{fig:exec1} shows how the corresponding security context
develops over the first few steps of the program, beginning with
the start of {\tt main} (\(\PCname = 0\)) and with the stack pointer at address 1000.
State transitions are numbered and labeled with a list of security operations, written
\(\downarrow \overline{\psi}\) between steps.

@@

To begin with, what if {\tt f} returns to an unexpected place (i.e. \(\PCname \neq 20\) or
\(\SP \neq 980\))? We consider this to
violate well-bracketed control flow (WBCF). WBCF is a relationship between
call steps and their corresponding return steps: just after the return, the program
counter should be at the next instruction following the call,
and the stack pointer should be the same as it was before the call.

@@

To see why WBCF also cares about the stack pointer, consider the attack in
Figure \ref{subfig:WBCF2}. Here the attacker returns with \(\SP' = 998\) instead of the
correct \(\SP = 980\). In this scenario, given the layout of {\tt main}'s frame,
\begin{center}
\begin{tabular}{| l | l | l | l | l |}
  \multicolumn{1}{r}{\(\SP \downarrow\)} &
  \multicolumn{2}{r}{\(\SP' \downarrow\)} \\
  \hline
  res & sens & sec & ra & ra \\
  \hline
\end{tabular}
\end{center}

@@

In typical compiled code, WBCF is maintained by the compiler's call and return sequences.
As long as a function deallocates the same-sized frame that it allocates, and properly
saves and restores the return address, it should have WBCF---unless an error in the middle
subverts those sequences by overwriting one of the relevant elements, or by jumping into
the middle of the call or return sequence. We can therefore enforce WBCF by (1) ensuring that
these ``blessed'' call and return sequences execute in order and (2) permitting only blessed
sequences to write to \(\SP\), {\tt ra}, and the address in memory where {\tt ra} is stored.

To perform this enforcement using tags, we can take
\(\mathcal{T} ::= \mathit{gen} \mathrel{|} \mathit{bseq} ~ n ~ m \mathrel{|} \mathit{prot}\), named for general
execution, blessed sequence, and protected, respectively. Blessed sequences of length \(m\) are
tagged \(\mathit{bseq} ~ 1 ~ m\) through \(\mathit{bseq} ~ m ~ l\), and the micro-policy enforces
that they execute in order. The stack pointer and {\tt ra}
are tagged \(\mathit{prot}\). Only instructions tagged \(\mathit{bseq}\) may write to memory
or registers tagged \(\mathit{prot}\). Store instructions tagged \(\mathit{bseq}\) tag their
targets \(\mathit{prot}\).

@@

To characterize this situation in a property, we borrow the idea of \emph{variant} states
from the theory of non-interference.
For a set of elements \(\components\),
a pair of states \(\mach\) and \(\nach\) are {\em \(\components\)-variants} if
their values an only disagree on elements in \(\components\). We further require that
the respective values in \(\components\) be \emph{compatible}, meaning that even though
their payloads may differ, their tags (or whatever other data is important to
the machine's security enforcement mechanism) must be identical.

We say that the elements of \(\components\) are \emph{irrelevant}
in \(\mach\) if they can be replaced by compatible values without changing the
observable behavior of the machine. (We will formalize this in Section~\ref{sec:events}
by saying that every \(\components\)-variant state produces
an equivalent observation trace.) All other elements are \emph{relevant}.
We characterize \emph{observational integrity} as the property that
every relevant element that is \(\sealed\) under the callee's view is restored
to its original value at the return point.

@@

Consider the state \(\mach\) after step 5, whose context is \((V_2,\sigma)\), with the attacker from
Figure \ref{subfig:direct}. We take a variant state over the set of element(s) that are
\(\sealed\) or \(\unsealed\) in \(V_2\), which happens to be the entire stack (see
Figure \ref{fig:variant2}.) If we take a trace of execution from each state until it returns,
the traces may differ, in this case outputting 5 (the original value of {\tt secret}) and
4 (its value in the variant) respectively. This is a violation of
{\it internal confidentiality}.

@@

But, in Figure \ref{subfig:indirect}, we also saw an attacker that exfiltrated the secret
by reading it and then returning it, in a context where the caller would output the returned
value. Figure \ref{fig:variant3} shows the behavior of the same variants under this attacker,
but in this case, there is no output during the call. Instead the value of {\tt secret} is
extracted and placed in {\tt a0}, the return value register. We wish to identify this as
a confidentiality violation, again by considering variants of the \(\sealed\) and \(\unsealed\)
elements in \(V_2\), but capturing the required property is subtle.

@@

But in the case of {\tt a0}, the value has changed during the call (in both the original
and the variant, although only one of these would be necessary), and its final value
differs between the variants.
Therefore, it must depend on a secret (in fact, the variable {\tt secret}).
Unless {\tt a0} happens to be irrelevant, this is a violation of what
we term {\it return-time confidentiality}.

@@

Finally, we define caller confidentiality as the
combination of internal and return-time confidentiality.
While we have separated the definitions of integrity and confidentiality,
in terms of tag-based enforcement, Depth Isolation and Lazy Tagging and Clearing
both enforce both properties.

\paragraph*{Callee Confidentiality}

Although we presented our initial example from the perspective of the caller, a callee
may also have data that must be kept secret from its caller. Consider a callee that makes
a privileged system call to obtain a secret key, and uses that key to perform a specific
task. An untrustworthy or erroneous caller might attempt to read the key out of the callee's
memory after return.

We model this as nearly dual to caller integrity: the callee's secrets are those
values that it has stored in \(\unsealed\) elements. So, callee confidentiality means that
at the state following the callee's return, any relevant element that was \(\unsealed\) under
the callee's view retains its original value.

Once again, both tag-based approaches do enforce callee confidentiality, but it is
worth keeping separate because some enforcement mechanisms might not, and it has not
historically been acknowledged by all formal treatments of stack safety \cite{Georges22:TempsDesCerise}.

@@

The forms of stack safety described above are largely independent of one another, and
can potentially be enforced separately in various combinations. This is important, because
many existing enforcement mechanisms enforce only some of the stack safety
properties. Stricter enforcement may have greater performance impacts, leading to decisions
about trade-offs between different degrees of stack safety.

In principle, these properties can exist in any combination, but in practice we see examples
of certain combinations that form a hierarchy. Many enforcement techniques focus purely on
well-bracketed control flow. Stack canaries aim to prevent certain attacks on the return
address, and shadow stacks with protection (e.g. Return Address Defender \cite{Chiueh2001RAD})
to enforce it completely.

Others combine this protection with some degree of memory protection,
chiefly focusing on integrity. Skorstengaard et al. \cite{SkorstengaardSTK} characterize stack
safety as the combination of WBCF and {\it local state encapsulation} (LSE), and prove that their
capability-based enforcement satisfies both. LSE corresponds to integrity, plus the
confidentiality of the caller's frame, but not of the unallocated stack or data left
behind in it by previous callees.
They offer a fully abstract overlay semantics, which formalizes WBCF and LSE
together as a safe-by-construction abstract machine. That machine does not allow a callee to
read or write its caller's frame, but might allow it to read data that is left behind below
the caller's frame, which is weaker than our full caller confidentiality and rules out
callee confidentiality entirely. Georges et al. \cite{Georges22:TempsDesCerises} correct
both limitations.\bcp{Then why are we not comparing to them instead??}

@@

\paragraph*{Terminology and Notation}

@@

@@

[TODO: back-propagate abbreviations used here]

Finally, we can define our core properties. They can be found in \cref{tbl:props},
arranged to show their commonalities and distinctions. Each definition gives a criterion
quantified over states \(s\) that immediately follow call (or tail-call) steps.
If an execution can reach a state \(s\) such that \(s \stepstounder{\overline{\psi}} s'\)
where \(\mathbf{call} ~ \addr ~ \overline{\reg} \in \bar{\psi}\), then \(s'\) is the target
of a call. Likewise, if \(\mathbf{tailcall} ~ \addr ~ \overline{\reg} \in \bar{\psi}\), then
\(s'\) is the target of a tailcall. As a shorthand, we write that each property is defined
by a criterion that must hold ``when \(s'\) is called,'' i.e., for every such \(s'\).

@@

\begin{table*}[h]
  \begin{align*}
    \wbcf \triangleq & |\sigma| \uparrow \ret
    && \textnormal{ where } \ret ~ \mach' \textnormal{ iff }
    \mach'[\SP] = \mach[\SP] \land \mach'[\PCname] = \mach[\PCname]+4\}
    && \textnormal{ when } (\mach,(V,\sigma)) \textnormal{ is called} \\
    %
    \clri \triangleq & (|\sigma| \uparrow \intProp) ~ (\mach,(V,\sigma))
    && \textnormal{ where } \intProp ~ \mach' \textnormal{ iff }
    \mach' \parallel \sealed(V) \cap \Delta(\mach,\mach')
    && \textnormal{ when } (\mach,(V,\sigma)) \textnormal{ is called} \\
    %
    \clrc \triangleq & \forall \nach \textnormal{ s.t. } \mach \approx_{\sealed(V)} \nach, &&
    && \textnormal{ when } (\mach,(V,\sigma)) \textnormal{ is (tail)called} \\
    & |\sigma| \hookrightarrow (\mach,(V,\sigma)) \simeq |\sigma| \hookrightarrow (\nach,(V,\sigma)) \\
    & \textnormal{ and } (\mach,(V,\sigma)) ~ (|\sigma| \Uparrow \confProp) ~ (\nach,(V,\sigma))
    && \textnormal{ where } (\mach' ~ \confProp ~ \nach') \textnormal{ iff }
    \mach' \parallel \bar{\Diamond}(\mach,\nach,\mach',\nach') \\
    %
    \clec \triangleq & (|\sigma| \uparrow \cconfProp) ~ (\mach,(V,\sigma))
    && \textnormal{ where } \cconfProp ~ \mach' \textnormal{ iff }
    \mach' \parallel \unsealed(V) \cap \Delta(\mach,\mach')
    && \textnormal{ when } (\mach,(V,\sigma)) \textnormal{ is (tail)called} \\
    %
    \clei \triangleq & \forall \nach \textnormal{ s.t. } \mach \approx_{\unsealed(V)} \nach, &&
    && \textnormal{ when } (\mach,(V,\sigma)) \textnormal{ is (tail)called} \\
    & |\sigma| \hookrightarrow (\mach,(V,\sigma)) \simeq |\sigma| \hookrightarrow (\nach,(V,\sigma)) \\
    & \textnormal{ and } (\mach,(V,\sigma)) ~ (|\sigma| \Uparrow \confProp) ~ (\nach,(V,\sigma))
    && \textnormal{ where } (\mach' ~ \cintProp ~ \nach') \textnormal{ iff }
    \mach' \parallel \bar{\Diamond}(\mach,\nach,\mach',\nach') \\
  \end{align*}
  \caption{Properties}
  \label{tbl:props}
\end{table*}

[TODO: words about the complementary properties.]

@@

>>>>

We propose a novel characterization of stack safety using the formal tools of language-based
security~\cite{sabelfeld2003language}, decomposing stack safety into
the {\em integrity} and {\em confidentiality} of the caller’s local state
and the callee's behavior during the callee's execution, plus the control flow protection
of {\em well-bracketed control flow}~\cite{SkorstengaardSTKJFP} (\(\wbcf\)).
\ifexceptions
We also extend WBCF to a setting with exceptions,
in which there may be multiple points at which a callee can ``return.''
\fi

This gives us a total of five core properties: \(\wbcf\)
caller integrity (\(\clri\)), caller confidentiality (\(\clrc\)),
callee integrity (\(\clei\)), and callee confidentiality (\(\clec\)).

@@

We treat stack safety as multiple properties, rather than one multi-faceted property, because
not all enforcement mechanisms attempt to implement all aspects of stack safety. Some focus
exclusively on control flow, some enforce integrity but not confidentiality, and many
focus on the caller over the callee.

@@

Roessler and DeHon find that the intuitive way to enforce stack safety in this setting
is inefficient when allocating and clearing stack frames, because each word must be initialized
with a tag corresponding to the (depth of the) current function activation. They propose
{\em Lazy Tagging and Clearing}, in which tags are not initialized at allocation, but only
when a function writes to memory. This means that writes cannot be prevented, necessarily
violating existing models of stack safety. Instead the micro-policy enforces that memory be
read by the same fuction that wrote it. The owner of the data will never see the changes,
so it is secure in the sense that the attacker is unsuccessful at changing program behavior
(except, perhaps, by causing a fault.) We elaborate that sense, and test whether the
micro-policy fulfills it.

This key motivation leads us to present integrity and confidentiality as predicates on (pairs of)
machine states that make claims about the future observable behavior of execution from those states.
That is not to say that our properties are specialized for lazy micro-policies. It also supports
normal ``eager'' micro-policies, and should support other enforcement mechanisms. In fact, \(\clri\)
and \(\clrc\) are even weaker than necessary to support Roessler and Dehon's micro-policy,
while \(\clec\) and \(\clei\) are stronger properties that they do not attempt to enforce.

@@

\begin{itemize}
\item We formalize permissive stack confidentiality and integrity properties,
  which are parameterized over a notion of external
  observation, and are violated only if accessing secrets or overwriting
  data causes a visible change in system behavior.
\item We instantiate these definitions with a realistic
  system with features such as argument passing
  on the stack, callee-saves registers, and tail-call elimination.
  Our model is modular enough that adding these features is straightforward.
\item Our formalization of well-bracketed control flow in the presence of tail-call
  elimination \ifexceptions and exceptions \fi is a novelty over existing models.
\item We use property-based random testing to validate the relationship between
  our properties and micro-policies.
\end{itemize}

@@

The set of security-relevant operations (\(\Psi\)) covered in this paper is given in
\cref{tab:psi}. Those that we explore in detail in \cref{sec:example}
are shown in white: calls, returns, and the allocation and deallocation of local memory.
In \cref{sec:machine}), we cover additional operations that add parameters to the examples',
to support various forms of memory sharing \ifexceptions , exceptions, \fi
and tail-call elimination. These are shown in light gray.
We give a proof-of-concept formalization of a more sophisticated, heap-like sharing model
based on pointer provenance in \cref{app:ptr}, represented by the dark grey
operations, but we do not test this.

@@

\sna{Might like a better name than object, because morally it ought to apply to arguments as well.}

@@

The properties form a hierarchy, shown in [TODO: diagram].
Within properties that are orthogonal
some are likely to take priority in terms of their
importance to security. Almost all stack-safety enforcement mechanisms will try to enforce \(WBCF\),
as control-flow attacks such as ROP are a major vulnerability that can be targeted via the stack.
Many also cover some degree of (caller) integrity. Caller confidentiality has been fairly neglected,
and callee-oriented properties even moreso.

@@

Otherwise, we do not assume that the code adheres to any particular
calling convention or implements a source language construct.
In particular, while we are agnostic as to the source
language, we certainly aim to support C, and so any source function might contain undefined
behavior resulting in its compilation to arbitrary machine code. A given enforcement
mechanism may place additional constraints, particularly on the behavior of
call and return sequences. For instance, extant implementations tend to assume
implicitly that callee-saved registers are treated appropriately by whichever compiler
generated their code. Our properties explicitly require them to be treated as belonging
to the caller, which could be enforced by a micro-policy or by a well-behaved compiler.

@@

The security semantics for this program is based
on the security-relevant events noted in the right columns of Figures~\ref{fig:main}
and~\ref{fig:f}, namely execution of instructions that allocate or deallocate space,
make a call, or make a return.

Recall that our security semantics attach a security context to the machine state,
which consists of a view \(V\) and a stack \(\sigma\) of pending activations' views.
(See \cref{sec:machine} for details.)
Figure \ref{fig:exec1} shows how the security context develops over the first few
steps of the program, according to the rules in \cref{fig:advops}, slightly simplified.
It begins at the start of {\tt main}, where the program counter (\(\PCname\)) is zero,
and with the stack pointer (\(\SP\)) at address 1000.
State transitions are numbered and labeled with a list of security operations, written
\(\downarrow \overline{\psi}\) between steps.

@@

To begin with, what if {\tt f} returns to an unexpected place (i.e. \(\PCname \neq 20\) or
\(\SP \neq 980\))? We consider this to violate \(\wbcf\). \(\wbcf\) is a relationship between
call steps and their corresponding return steps: just after the return, the program
counter should be at the next instruction following the call,
and the stack pointer should be the same as it was before the call.

@@

To see why \(\wbcf\) also cares about the stack pointer, consider the attack in
Figure \ref{subfig:WBCF2}. Here the attacker returns with \(\SP' = 998\) instead of the
correct \(\SP = 980\). In this scenario, given the layout of {\tt main}'s frame,
\begin{center}
\begin{tabular}{| l | l | l | l | l |}
  \multicolumn{1}{r}{\(\SP \downarrow\)} &
  \multicolumn{2}{r}{\(\SP' \downarrow\)} \\
  \hline
  res & sens & sec & ra & ra \\
  \hline
\end{tabular}
\end{center}

@@

@@

To characterize this situation in a property, we borrow the idea of \emph{variant} states
from the theory of non-interference. For a set of elements \(\components\),
a pair of states \(\mach\) and \(\nach\) are {\em \(\components\)-variants} if
their values an only disagree on elements in \(\components\). We further require that
the respective values in \(\components\) be \emph{compatible}, meaning that even though
their payloads may differ, their tags (or whatever other data is important to
the machine's security enforcement mechanism) must be identical.
We say that the elements of \(\components\) are \emph{irrelevant}
in \(\mach\) if they can be replaced by compatible values without changing the
observable behavior of the machine. All other elements are \emph{relevant}.
Variants and relevance are defined in \cref{sec:props}.

We characterize \(\clri\) as the property that
every relevant element that is \(\sealed\) under the callee's view is restored
to its original value at the return point.

@@

Consider the state \(\mach\) after step 5, whose context is \((V_2,\sigma)\), with the attacker from
Figure \ref{subfig:direct}. We take a variant state over the set of element(s) that are
\(\sealed\) in \(V_2\) (see Figure \ref{fig:variant2}.)
            [TODO: fix figure to avoid varying the entire stack.]
If we take a trace of execution from each state until it returns,
the traces may differ, in this case outputting 5 (the original value of {\tt secret}) and
4 (its value in the variant) respectively. This is a violation of
{\it internal confidentiality} (\cref{tab:props}, line 3a.)

@@

But, in Figure \ref{subfig:indirect}, we also saw an attacker that exfiltrated the secret
by reading it and then returning it, in a context where the caller would output the returned
value. Figure \ref{fig:variant3} shows the behavior of the same variants under this attacker,
but in this case, there is no output during the call. Instead the value of {\tt secret} is
extracted and placed in {\tt a0}, the return value register. We wish to identify this as
a confidentiality violation, again by considering variants of the \(\sealed\)
elements in \(V_2\), but capturing the required property is subtle.

@@

But in the case of {\tt a0}, the value has changed during the call (in both the original
and the variant, although only one of these would be necessary), and its final value
differs between the variants.
Therefore, it must depend on a secret (in fact, the variable {\tt secret}).
Unless {\tt a0} happens to be irrelevant, this is a violation of what
we term {\it return-time confidentiality} (\cref{tab:props}, line 3b.)

@@

Finally, we define \(\clrc\) as the
combination of internal and return-time confidentiality.

\paragraph*{The Callee's Perspective}

We presented our initial example from the perspective of the caller, a callee
may also have privilege that its caller lacks, and which must be protected from the
caller. Consider a function that makes a privileged system call to obtain a secret key,
and uses that key to perform a specific task. An untrustworthy or erroneous caller might
attempt to read the key out of the callee's memory after return, or to influence the callee
to cause it to misuse the key itself!

Where the caller's confidentiality and integrity are concerned with protecting specific,
identifiable state---the caller's stack frame---their callee equivalents are concerned
with enforcing the expected interface between caller and callee. Communication between
the principals should occur only through the state elements that are designated for the
purpose: those which we label \(\public\) and (in the presence of memory sharing) \(\object\).

The properties themselves correspond to their caller equivalents, inverted.

@@

The forms of stack safety described above can potentially be enforced separately
in various combinations. This is important, because
many existing enforcement mechanisms enforce only some of the stack safety
properties. Stricter enforcement may have greater performance impacts, leading to decisions
about trade-offs between different degrees of stack safety.

 \(\clec\) subsumes \(\clri\), and \(\clei\) subsumes
\(\clrc\), but integrity and confidentiality are in general orthogonal to each other
and to \(\wbcf\). Despite this, many enforcement techniques focus purely on
well-bracketed control flow. Stack canaries aim to prevent certain attacks on the return
address, and shadow stacks with protection (e.g. Return Address Defender \cite{Chiueh2001RAD})
to enforce it completely. Others combine this protection with some degree of memory protection,
chiefly focusing on integrity.

@@

@@

[TODO: this section could use some trimming. I think we have room for this
discussion, it's just more verbose than everything else and therefore feels weird.]

@@

Finally, we can define our core properties. They can be found in \cref{tab:props},
arranged to show their commonalities and distinctions. Each definition gives a criterion
quantified over states \(s\) that immediately follow call (or tail-call) steps.
If an execution can reach a state \(s\) such that \(s \stepstounder{\overline{\psi}} s'\)
where \(\mathbf{call} ~ \addr ~ \overline{\reg} \in \bar{\psi}\), then \(s'\) is the target
of a call. Likewise, if \(\mathbf{tailcall} ~ \addr ~ \overline{\reg} \in \bar{\psi}\), then
\(s'\) is the target of a tailcall. As a shorthand, we write that each property is defined
by a criterion that must hold ``when \(s'\) is called,'' i.e., for every such \(s'\).

@@

\begin{table*}[h]
  \setlength{\tabcolsep}{1pt}
  \center
  \begin{tabular}{l r l l l}
    \rowcolor{black!20}
    1
    & \(\wbcf \triangleq\) & \(|\sigma| \uparrow \ret\)
    & \(\textnormal{ where } \ret ~ \mach' \textnormal{ iff }\)
    \(\mach'[\SP] = \mach[\SP] \land \mach'[\PCname] = \mach[\PCname]+4\)
    & \(\textnormal{ when } (\mach,(V,\sigma)) \textnormal{ is called}\) \\
    %
    \rowcolor{black!10}
    2
    & \(\clri \triangleq\) & \((|\sigma| \uparrow \intProp) ~ (\mach,(V,\sigma))\)
    & \(\textnormal{ where } \intProp ~ \mach' \textnormal{ iff }
    \mach' \parallel \sealed(V) \cap \Delta(\mach,\mach')\)
    & \(\textnormal{ when } (\mach,(V,\sigma)) \textnormal{ is called}\) \\
    %
    \rowcolor{black!20}
    3
    & \(\clrc \triangleq\) & \(\forall \nach \textnormal{ s.t. } \mach \approx_{\components} \nach,\)
    & \(\textnormal{ where } \components = \sealed(V)\)
    & \(\textnormal{ when } (\mach,(V,\sigma)) \textnormal{ is (tail)called}\) \\
    \rowcolor{black!20}
    3a & & \(|\sigma| \hookrightarrow (\mach,(V,\sigma)) \simeq |\sigma| \hookrightarrow (\nach,(V,\sigma))\) & & \\
    \rowcolor{black!20}
    3b & & \(\textnormal{ and } (\mach,(V,\sigma)) ~ (|\sigma| \Uparrow \confProp) ~ (\nach,(V,\sigma))\)
    & \(\textnormal{ where } (\mach' ~ \confProp ~ \nach') \textnormal{ iff }
    \mach' \parallel \bar{\Diamond}(\mach,\nach,\mach',\nach')\) & \\
    %
    \rowcolor{black!10}
    4
    & \(\clec \triangleq\) & \((|\sigma| \uparrow \cconfProp) ~ (\mach,(V,\sigma))\)
    & \(\textnormal{ where } \cconfProp ~ \mach' \textnormal{ iff }
    \mach' \parallel \Delta(\mach,\mach') - \components\)
    & \(\textnormal{ when } (\mach,(V,\sigma)) \textnormal{ is (tail)called}\) \\
    \rowcolor{black!10}
    & & & \(\textnormal{ where } \components = \public(V) \cup \object(V)\) & \\
    %
    \rowcolor{black!20}
    5
    & \(\clei \triangleq & \forall \nach \textnormal{ s.t. } \mach \approx_{\components} \nach,\)
    & \(\textnormal{ where } \components = \public(V) \cup \object(V)\)
    & \(\textnormal{ when } (\mach,(V,\sigma)) \textnormal{ is (tail)called}\) \\
    \rowcolor{black!20}
    5a & & \(|\sigma| \hookrightarrow (\mach,(V,\sigma)) \simeq |\sigma| \hookrightarrow (\nach,(V,\sigma))\) & & \\
    \rowcolor{black!20}
    5b & & \(\textnormal{ and } (\mach,(V,\sigma)) ~ (|\sigma| \Uparrow \confProp) ~ (\nach,(V,\sigma))\)
    & \(\textnormal{ where } (\mach' ~ \cintProp ~ \nach') \textnormal{ iff }
    \mach' \parallel \bar{\Diamond}(\mach,\nach,\mach',\nach')\) & \\
  \end{tabular}
  \caption{Properties}
  \label{tab:props}
\end{table*}

@@

[TODO: this is still last submission's test. Kept here to get a sense of length.]
